How is the Brazilian Amazon constructed as a problem at different levels? Amazonian

### 2022-02-11 20220210_Draft.Rmd
#fewchangestodictionary

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|dono|internacionalizar|fronteira")

@@

conservation <- ("preserv|conserv|determinacao|povos indigenas|demarcar|queimada|sustentav|meio ambiente|florest|protecao|proteg|renovavel|garantias ambientais|garantia ambiental|reduzir desmatamento|combate ao desmatamento|combater desmatamento|baixo carbono|limpa|direitosambientais")

>>>>

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|soberana|soberano|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|exercito|dono|internacionalizar| |internacionalizacao")

@@

conservation <- ("preserv|conserv|determinacao|povos indigenas|demarcar|meio ambiente|protecao|proteg|renovavel|garantias ambientais|garantia ambiental|reduzir desmatamento|combate ao desmatamento|combater desmatamento|baixo carbono|limpa|direitos ambientais|unidades de conservacao")
